
FACTORIAL TWO WAY REPEATED MEASURES ANOVA


```{r}
library(lme4)
library(nlme)

LateLPP.data <- read.csv("LateLPPdata.csv", header = TRUE)
LateLPP.data$Social.condition <- as.factor(LateLPP.data$Social.condition)
LateLPP.data <- LateLPP.data[complete.cases(LateLPP.data), ]
LateLPP.data


model <- lme(Avg..amplitude ~ Social.condition * Emotional.condition, random=~1|Subject, data = LateLPP.data)
anova(model)

library(car)
model1 <- lmer(Avg..amplitude ~ Social.condition + Emotional.condition + Social.condition:Emotional.condition+(1|Subject), data = LateLPP.data)
Anova(model1, type = 'II')

```
From the p-values and F-values it can be interpreted that there is a main effect of the social and emotional condition

POST HOC TEST FOR MAIN EFFECTS OF EMOTIONAL AND SOCIAL CONDITION

Main effect of social condition
```{r}
library(emmeans)

emm <- emmeans(model1, pairwise ~ Social.condition)
print(emm)


```

Main effect of emotion
```{r}
emm1<- emmeans(model1, pairwise ~ Emotional.condition)
print(emm1)
```

Significant difference between (224, 225) and (224, 231)
Significant difference between (Happy and Neutral)
224 = Shared with feedback, 225 = Shared without feedback, 231 = Unshared




