
FACTORIAL TWO WAY REPEATED MEASURES ANOVA

```{r}
library(lme4)
library(nlme)

EarlyLPP.data <- read.csv("EarlyLPPdata.csv", header = TRUE)
EarlyLPP.data$Social.condition <- as.factor(EarlyLPP.data$Social.condition)
EarlyLPP.data <- EarlyLPP.data[complete.cases(EarlyLPP.data), ]
EarlyLPP.data


model <- lme(Avg..amplitude ~ Social.condition * Emotional.condition, random=~1|Subject, data = EarlyLPP.data)
anova(model)

library(car)
model1 <- lmer(Avg..amplitude ~ Social.condition + Emotional.condition + Social.condition:Emotional.condition+(1|Subject), data = EarlyLPP.data)
Anova(model1, type = 'II')

```
Main effect of social condition
```{r}
library(emmeans)

emm <- emmeans(model1, pairwise ~ Social.condition)
print(emm)


```

Main effect of emotion
```{r}
emm1<- emmeans(model1, pairwise ~ Emotional.condition)
print(emm1)



```

Main effect of social
```{r}
emm2<- emmeans(model1, pairwise ~ Social.condition*Emotional.condition)
pairs(emm2, simple = "each")$emmeans
```



 of Significant difference between (224, 225) and (224, 231)
 
 
 Top down effect carries over to later stages of processing
 Shared with feedback enhances arousal towards emotional 
 
 
Significant difference between (Neutral and Happy)


replicates previous literature


Within angry there is a difference between all social levels
Within social condition 231 (unshared) there is a significant difference between (Angry,Neutral) and (Happy,Neutral)

224 = Shared with feedback, 225 = Shared without feedback, 231 = Unshared


Especially effect on the angry condition where a social condition has an effect. It does not seem to have an effect on


