
FACTORIAL TWO WAY REPEATED MEASURES ANOVA

```{r}
library(lme4)
library(nlme)

N170.data <- read.csv("N170data.csv", header = TRUE)
N170.data$Social.condition <- as.factor(N170.data$Social.condition)
N170.data <- N170.data[complete.cases(N170.data), ]
N170.data


model <- lme(Avg..amplitude ~ Social.condition * Emotional.condition, random=~1|Subject, data = N170.data)
anova(model)

#library(car)
#model1 <- lmer(Avg..amplitude ~ Social.condition + Emotional.condition + Social.condition:Emotional.condition+(1|Subject), data = N170.data)
#Anova(model1, type = 'II')

```

From the p-values and F-values it can be interpreted that there is a main effect of the social and emotional condition

POST HOC TEST FOR MAIN EFFECTS OF EMOTIONAL AND SOCIAL CONDITION

```{r}
library(emmeans)

emm <- emmeans(model1, pairwise ~ Social.condition)
print(emm)
emm1<- emmeans(model1, pairwise ~ Emotional.condition)
print(emm1)

#pairs(emm, simple = "each")$emmeans

```
Significant difference between (224, 225) and (224, 231)

Top doen effect of feedback from other person
the top down effect enhances structural (encoding)
Top down effect of shared attention on structural processing of faces (N170)

N170 more attention
LPP more arousal
Hypothesize we expect the social context
does feedback have a further top down effect.

Significant difference between (Angry and Happy)

We would have expected differences between all three

224 = Shared with feedback, 225 = Shared without feedback, 231 = Unshared








